BurgerTown Presents: Open Adcess

### 2017-06-23 ideas.tex
gametes trial version

>>>>

The ACM is a meritocracy. No limits imposed at birth follow our citizens through the rest of their lives. For instance, any person created using Gametes Trial Version can choose to pay to upgrade their membership and unlock hidden features, such as the ability to jump and the ability to make out the lyrics to Neil Young's \emph{The Monsanto Years} and Buffy Sainte-Marie's \emph{Power in the Blood}. Our (patented gene-editing technology) will enable trial members to eliminate the Trial Version melanin stamp on their forehead or even to remove their fingers and their thumbs in the shape of an L from their forehead.
